---
title: 'TP3: GuangYue Chen, Sovathana Soun, Eya Ben Khelifa'
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

Group Members: GuangYue Chen (n?45) ; Sovathana Soun (n?13) ; Eya Ben Khelifa (n?32);
On s'attribue la note de 3/3 S


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r,include=FALSE}
rm(list = ls())
library(ggplot2)
library(plot3D)
library(rasterVis)
```
#Exercice 1

###Q1 Implémentez l’algorithme précédent pour une configuration initiale S fixée.

```{r}
simu_init<-function(){
  X=c(-1,1)
  P=c(0.5,0.5)
  C<-c(P[1])
    C<-c(C,C[1]+P[2])

  k<-1
  u<-runif(1,0,1)
  while(u>C[k]){
    k<-k+1
  }
  return (X[k])
}

simu_runif<-function(N){
  c <- (1/N)
  P <- rep(c, N)#repeat c for N times
  C <- vector("numeric", N)
  C[1] = c
  for (i in 2:N) {
    c = c + P[i]
    C[i] = c
  }
  X <- as.numeric(1:N)
    k <- 1
  u <- runif(1,0,1)
  while(u>C[k]) {
    k <- k+1
  }
  return (X[k])
}




initialstate<-function(N){
  X<-c()
  for(i in 1:N^2){
    X<-c(X,simu_init())
  }
  state<-matrix(X,N,N)
return(state)
}



mcmove<-function(S, N,beta){
   
                a = simu_runif(N)
                b =  simu_runif(N)
                s_x <-  S[a, b]
                
                
                if(a==1){
                  s1=S[(a+1),b]
                  s3 =0
                  
                }else if(a==60){
                   s1=0
                   s3= S[(a-1),b]
                }else{
                  s1=S[(a+1),b]
                  s3= S[(a-1),b]
                }
                
                
                if(b==1){
                  s2=S[a,(b+1)] 
                  s4 =0
                }else if(b==60){
                  s2=0
                  s4= S[a,(b-1)]
                }else{
                  s2=S[a,(b+1)] 
                  s4= S[a,(b-1)]
                }
                
                delta_H = 2*s_x*(s1+s2+s3+s4)
                u=runif(1,0,1)

               
                 if( u <= exp(-delta_H*beta) ){
                   s_x =s_x*(-1)
                }
               
                S[a, b] = s_x
      
  return (S)
}


Simulation<-function(S_init,N,beta,times){
  
S<-S_init

for(i in 1:times){
  S<-mcmove(S,N,beta)
}
return(S)
}

```

```{r}
S_init<-initialstate(60)
S1=Simulation(S_init,60,0.1,times=30000)
S2=Simulation(S_init,60,0.1,times=30000)
S3=Simulation(S_init,60,0.1,times=30000)
levelplot(S1)
levelplot(S2)
levelplot(S3)
```



###Q2
```{r}
S4=Simulation(S_init,60,10,times=30000)
S5=Simulation(S_init,60,10,times=30000)
S6=Simulation(S_init,60,10,times=30000)
levelplot(S4)
levelplot(S5)
levelplot(S6)
```
###Q3
We can see that with a low beta of 0.1 the spins are very dispersed. Which is accurate because when beta is low, the temperature T=1/beta is high. And a high temperature results in a distribution of the spins that is untidy.
We can see on the contrary that with a high beta of 10 the spins are more ordered. Which is again very accurate since when we have a high beta the temerature is low. So the spins' distribution is more tidy.



###Q4

```{r}
S_init2<-initialstate(60)
S7=Simulation(S_init2,60,10,times=30000)
S8=Simulation(S_init2,60,10,times=30000)
S9=Simulation(S_init2,60,10,times=30000)
levelplot(S7)
levelplot(S8)
levelplot(S9)

```
We can see that we have the same observations: When beta is low the spins are dispersed and when beta is high we have a more homogenous distribution.

#Exercice 2.
```{r}
#lire le fichier 
sigma_0<-read.csv("Coordonnees-Villes.csv")

H<-function(sigma){
  sum=0
  N<-dim(sigma)[1]
  for(i in 2:N){
    sum=sum+sqrt((sigma[i,2]-sigma[i-1,2])^2+(sigma[i,3]-sigma[i-1,3])^2)
  }
   sum=sum+sqrt((sigma[N,2]-sigma[1,2])^2+(sigma[N,3]-sigma[1,3])^2)
  return(sum)
}

H(sigma_0)
```
```{r}

simu_omega<-function(sigma){
  N<-dim(sigma)[1]
  i<-simu_runif(N)
  k<-simu_runif(N)
  if(i==k){
    
  }else{
    couple=sigma[i,]
    sigma[i,]=sigma[k,]
    sigma[k,]=couple
  }
  return(sigma)
}

e2move<-function(sigma,omega,c,time){
  u<-runif(1,0,1)
  beta<-c*log(time+1)
  if(u<=exp(-beta*(H(omega)-H(sigma)))){
    sigma=omega
  }
  return(sigma)
}


Simulation2<-function(sigma,c,times){
 
for(i in 1:times){
  omega<-simu_omega(sigma)
  sigma<-e2move(sigma,omega,c,i)
}
return(sigma)
}


```
```{r}
res<-Simulation2(sigma_0,10,100000)
res
H(res)
```

Donc apres cet algorithme, le valeur de H est bien diminue.