---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#E1 Compute the partition matrix
###compute the matrix C = (cik) where cik = 1 if i belong to K 
```{r r include=TRUE}
library("nnet")
data(iris)
X <- iris[, 1 : 4]
cluster <-iris$Species
C <- class.ind(cl=cluster)
```
###compute the gravity centers
```{r r include=TRUE}
#矩阵做法
M <- matrix(data = 0, nrow = 3, ncol = 4)
as.matrix(X) -> X

solve((t(C)%*%C))%*%t(C)%*%X

#循环算法
M <- matrix(0, ncol(C), ncol(X))
for(i in 1:nrow(X)) {
  M[which.max(C[i,]),] <- M[which.max(C[i,]),] + X[i,]
}

M <- t(t(M) / colSums(C))
M
```












#E4 Clustering of crabs
###Q1 load crab data from MASS
```{r r include=TRUE}
rm(list = ls())
library(MASS)
data(crabs)
```
###Q2 represent all crabs with a color corresponding to the specy and a spmpol to the sex
```{r r include=TRUE}
C <- class.ind(cl=crabs$sp)
plot(crabs)
pairs(crabs)




#前面只是用来比较，下面正确做法
pairs(crabs, col = c("blue", "orange")[crabs$sp],pch = c(20, 21)[crabs$sex])
#c("a", "b")[c(1, 1, 2, 1)] = aaba
crabsquant = crabs[,4:8]
pairs(crabsquant, col = c("blue", "orange")[crabs$sp],pch = c(20, 21)[crabs$sex])
```
###Q3 using kmeans
```{r r include=TRUE}
kmeans(crabsquant, 4) -> res
res$cluster
paste(crabs$sp, "-", crabs$sex) -> True_Class
True_Class
str(res)

```
###Q4 within sum of square 
```{r r include=TRUE}
#within sum of square 
res$tot.withinss
table(True_Class,res$cluster)
pairs(crabsquant, col = c("blue", "orange","red","black")[res$cluster],pch = c(20, 21)[crabs$sex])
```
#未标准化出现较大误差 ， 取出总大小进行标准化
```{r r include=TRUE} 
crabsquant2<-crabsquant[,-3]/crabsquant$CL #pour enlever l'effet de la taille
kmeans(crabsquant2, 4) -> res
res$cluster
paste(crabs$sp, crabs$sex, "-") -> True_Class
table(True_Class,res$cluster)
pairs(crabsquant, col = c("blue", "orange","red","black")[res$cluster],pch = c(20, 21)[crabs$sex])
```
#run the kmeans 1000 times and keep track of Iw  ,within sum of square 
```{r r include=TRUE}
hist(mapply(function(x){kmeans(crabsquant, 4, nstart = 1)$tot.withinss},1:1000))
hist(mapply(function(x){kmeans(crabsquant2, 4, nstart = 1)$tot.withinss},1:1000))

kmeans(crabsquant2, 4, nstart = 30)->res.kmeans2
table(True_Class, res.kmeans2$cluster)


```

```{r r include=TRUE}

#划分线
z<-kde2d(crabsquant2[,2],crabsquant2[,4])
contour(z)
#plot
points(crabsquant2[,c(2,4)],col=c("blue","orange")[crabs$sp],pch=c(20,21)[crabs$sex])
#中心
points(res.kmeans2$centers[,c(2,4)],cex=2,pch=21,bg="red")

```
#Q8 cluster to 1-20 clustering
```{r r include=TRUE}
plot(mapply(function(x){kmeans(crabsquant2,x,nstart = 20)$tot.withinss},1:20))
#四类时下降速度变慢
```





