---
title: "TD1. MAD"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1)
IQ~N(100, sigma = 15)
what is the prob of having a IQ >= 120, IQ <= 100?
Plot a figure illustrating the answers.

```{r include=TRUE}
IQ = rnorm(1000, mean = 100, sd = 15)
plot(IQ)
x = 0
y = 0
for(i in 1:1000) {
  if(IQ[i] >= 120){
    x = x+1
  }
  if(IQ[i] <= 100){
    y = y+1
  }
}
print("大于120概率")
x/1000
pnorm(120,100,15, lower.tail = FALSE) #大于120概率 lower.tail: P(X<=x) ou P(X>x)

print("小于100概率")
y/1000
pnorm(100,100,15)#小于100概率

#相当于标准化后的
1 - pnorm(4/3)
```

```{r include=TRUE}
require("ggplot2")
IQ.sup120 <- function(x) {
  ifelse(x>120, dnorm(x, mean = 100, sd = 15), NA)
}
IQ.sup120(130)
ggplot(data.frame(x = c(20, 180)), aes(x))+
        stat_function(fun = dnorm, args = list(mean = 100, sd = 15))+
         stat_function(fun = IQ.sup120, geom = "area", fill = "red")
#mapping methode:对x做后面的操作
```

#2

估计正太分布参数
```{r include=TRUE}
sigma = 10
n = 10
ns = 1000
estimation = matrix(0, ns, 2) #一千个0分两列

#估计mu和lambda
for(i in 1:ns) {
  x = rnorm(10)
  estimation[i, 1] = mean((x-mean(x))**2)
  estimation[i,1]*n/(n-1) -> estimation[i,2]
}
hist(estimation[,1], breaks = 50)
abline(v = 1)
colMeans(estimation) #列平均
```
#3
复合正态分布
```{r include=TRUE}
require("MASS")
mu = vector(length = 2)
mu[1] = 0
mu[2] = 0
sigma = matrix(0, 2, 2)
sigma[1,1] = 2
sigma[1,2] = 1
sigma[2,1] = 1
sigma[2,2] = 0.75
#mvrnorm(n = 1000, mu, Sigma = sigma)

#mvrnorm multi norm distribution：faut vectoriser
#corrige:
x = mvrnorm(1000, mu = as.vector(c(0,0)),Sigma = matrix(c(2,1,1,0.75),2,2))
plot(x)

```

```{r include=TRUE}
mu = as.vector(c(0,0))  
Sigma = matrix(c(2,1,1,0.75),2,2)
zz = outer(X = 1:100, Y = 1:100, function(x,y){x^2 + y^2})
persp(zz)
```

```{r include=TRUE}
mv2Ddensity <- function(x, y){
  mu <- as.vector(c(0,0))
  Sigma<-matrix(c(2,1,1,0.75),2,2)

  (2 + pi)**(-1)*det(sigma)**(-1/2)*exp(-1/2*(c(x,y)-mu)%*%solve(Sigma)%*%cbind(c(x,y)-mu))
}
mv2Ddensity <- function(x, y, mu = as.vector(c(0,0)),Sigma = matrix(c(2,1,1,0.75),2,2)){
  (2 + pi)**(-1)*det(sigma)**(-1/2)*exp(-1/2*(c(x,y)-mu)%*%solve(Sigma)%*%cbing(c(x,y)-mu))
}

z = outer(X = 1:100, Y = 1:100, mv2Ddensity(x, y))
persp(z)


```





















