---
title: "TD3 MAD"
output: html_document
---

```{r include=TRUE}

nks<-rmultinom(1,1000,prob=c(1/3,2/3))
means<-c(0,4)
sds<-c(1,1/2)
samples<-mapply(function(nk,mean,sd){rnorm(nk,mean,sd)},nks,means,sds)
hist(x<-unlist(samples))


curve(dnorm(x,mean=4,sd=1/2),-2,7,col="orange")
curve(dnorm(x,mean=0,sd=1),-2,7,add=TRUE,col="red")

mixture<-function(x){
  1/3*dnorm(x,mean=0,sd=1)+
    2/3*dnorm(x,mean=4,sd=1/2)
  }
curve(mixture(x), -2, 7, col="blue", add=TRUE)



```

```{r include=TRUE}
res.means<-kmeans(x, 2, nstart = 10)
list.of.cluster<-split(data.frame(x), res.means$cluster)
res.means
```

```{r include=TRUE}
library(mclust)
Mclust(x)->res
summary(res)

#summary(Mclust(x,modelNames = 'E'))#????????????bic
#summary(Mclust(x,modelNames = 'V'))#????????????bic
```

```{r include=TRUE}
Mclust(x, 2, modelNames = "V") -> res.2V
Mclust(x, 2, modelNames = "E") -> res.2E
```
###E2 Bi-dimensional mixture
```{r include=TRUE}
data(faithful)
plot(faithful)
```

```{r include=TRUE}
res_Mclust<-Mclust(faithful)
summary(res_Mclust)

```
So the number of cluster is 3.
```{r include=TRUE}
#res$z  #matrice of tik

res$parameters

res$classification #the classification

```

```{r include=TRUE}
plot(res,"BIC")
```
this plot discribe with different modelname , the results of BIC. We choose the k value which with the max BIC.
```{r include=TRUE}
plot(res,"classification")
```
this plot present the classification, different classes have different colors and shapes.
```{r include=TRUE}
plot(res,"uncertainty")
```
This plot show the uncertainty, same as the last on, the colors mean different classes, and if the point is bigger, this point is more uncertain.
```{r include=TRUE}
plot(res,"density")
```
this plot present the whole density of this data.

#5 run the hclust
```{r include=TRUE}
out.dist=dist(faithful,method="euclidean")  
res_hclust<-hclust(out.dist, method = "complete")
```

```{r include=TRUE}
summary(res_hclust)
```

```{r include=TRUE}
plot(res)
```

```{r include=TRUE}
cutree(res_hclust,3)->res_hclust.cluster
res_Mclust$classification->  res_Mclust.cluster
table(res_hclust.cluster,res_Mclust.cluster)
```

